The Impact of News Sentiment on MSFT

### 2023-12-09 MSFT.Rmd
Included news sentiment of testing period while predicting the future values

However, from a practical point of view, our VAR model may still be of some use when applied for forecasting purposes. To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy in predicting the price movements of MSFT we do some forecasting for our testing period.

@@

```{r echo=FALSE, include=TRUE}
forecast <- predict(MSFT_VAR, n.ahead = length(news_test))
plot(forecast)
MSFT_VAR_pred <- forecast$fcst$MSFT_Returns

>>>>

However, from a practical point of view, our VAR model may still be of some use when applied for forecasting purposes. To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the news sentiment data of the testing period.

@@

```{r echo=FALSE, include=TRUE}
forecast_data <- data.frame(
  MSFT_Returns = rep(NA, length(news_test)),
  News_Sentiment = news_test
)

forecast <- predict(MSFT_VAR, newdata = forecast_data, n.ahead=43)
plot(forecast)
MSFT_VAR_pred <- forecast$fcst$MSFT_Returns
